---
title: "QRM II Graded Assignment (6)"
subtitle: "Period 1, 2026"
author: "Sophie Thoolen, Clemence van Gils, Benthe Tromp en Roos Bakker "
date:  "`r format(Sys.Date(), '%d-%m-%Y')`"
output:
  pdf_document:
    number_sections: true
  html_document:
    df_print: paged

header-includes:
- "\\setcounter{section}{-1}"
- |
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{
    showspaces = false,
    showtabs = false,
    breaklines,
    commandchars=\\\{\}
format:
  html:
    code-overflow: wrap
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This assignment is to be completed in groups of 4-5. Further, all
students in your group need to be assigned to the same R tutorial group
(Friday's tutorial). You can sign yourself up for a group on Canvas.
Please do so
\textbf{before the start of your first R tutorial on Friday September 4th.}
You can use the Discussion Board in Canvas if you do not have a group
yet or if your group is incomplete.

The assignment has 5 parts, and each part corresponds to the course
material of that week (with the exclusion of week 6, for which there is
no R programming material).

You are supposed to hand in these assignments on Canvas at the following
dates:

- **Deadline 1** *Sunday September 27th, at 23:59pm*: you are supposed
  to hand in weeks 1, 2, and 3 of this assignment. This will determine
  18% of your overall course grade
- **Deadline 2** *Sunday October 11th, at 23:59pm*: you are supposed to
  hand in weeks 4, and 5 of this assignment. This will determine 12% of
  your overall course grade

The R tutorials (each Friday) will consist of two halves. During the
first half, you will discuss the tutorial exercises. These can be
downloaded separately from Canvas. During the second half, you can work
on this graded assignment within your own group. The purpose is that you
find out how to work with R for doing statistical analyses by yourself.
The tutorial exercises are meant to teach you basic commands to get you
started, but to answer the problem sets in this assignment, you might
need to research your own solutions, and use functions and commands not
described in the tutorial exercises. Learning how to solve your own
research problems is integral part of learning R. When you and your
group get stuck on how to approach an exercise, the hierarchy in finding
your way is as follows:

- use the concepts from the tutorial exercises;
- use the cheat sheets available on Canvas;
- use Google, YouTube, StackOverflow, or another website;
- ask the teacher.

The use of generative AI is \textbf{not} permitted and may result in a
grade of 0. See the AI protocol in the course manual for details.

To answer the assignment, you can simply fill out this R markdown
document. There are designated places which you can fill with R code.
There are also designated spaces for you to answer each question. Often,
the structure of an answer will be as follows. First, you type the R
code in the designated box. This will show how you analyzed the data to
get the answer to the question. Below the box for the R code, you will
then summarize your answer to the question, i.e. what are the
conclusions that you draw from the data analysis?

When handing in, you are supposed to submit this .Rmd file, and a
knitted version of this document. You can knit this document to pdf,
word, or html. Knitting to pdf requires you to have a .tex distribution
installed on your computer. Knitting to Word requires you to have Word
installed.

The exercises are designed such that you should be able to finish the
majority of them during the tutorial each week. If you are not able to
finish them fully during that time, you are expected to work on it in
your own time using the computers on campus or your own device. It is
best to meet as a group in-person when working together. If you want to
work remotely, github is a good platform to guarantee smooth
collaboration. Alternatively, you can email this .Rmd file back and
forth to one another as a group, but this is not recommended as it is
more cumbersome.

We encourage you to keep your code blocks, printing statements, and
final answers, as short as possible. In any case, there is a page limit
of 6 pages per week, which encompasses the total length of this document
which consists of the questions, your coding lines, and your answers.
When your answers to questions of the respective week exceed this page
limit, they will not be graded, resulting in zero points.

# Week 1

1.  Find the dataset “movies4.tsv” on Canvas. Describe your data set:
    How many observations does it have. How many variables are there?
    How many subjects? What consists of a subject? \textbf{[4 points]}

```{r}
#WRITE YOUR CODE HERE
movies <- read.delim("movies4.tsv", sep = "\t", header = TRUE)

#number observations
nrow(movies)
#number of variables 
ncol(movies)

head(movies)
str(movies)
summary (movies)

#number of subjects 
nrow(movies)
##checked if all observations are different
length(unique(movies$title))

```

**Your Answer:**

The dataset contains 808 observations and 19 variables. A subject is a
individual movie and each observation corresponds to a movie, identified
by the variable 'title'. Since there is no recurrence of the same movie
name, the number of subjects is equal to the number of observations.
(which is 808)

2.  Which of the following types of variables are present in your data
    set? (i) nominal; (ii) ordinal; (iii); continuous; (iv) discrete. If
    present, name one example of such a variable present in your data
    set. \textbf{[4 points]}

```{r answer 2}
#WRITE YOUR CODE HERE
##checking the variables
str(movies)
```

**Your Answer:**

The following types of variables are present in this data set:

- Nominal: Yes, for example the variable genre or language which are
  organized by category without a specific order.

- Ordinal: Yes, for example the variable release_month (stored as a
  number but represents a month). This gives it a way to be ordered by
  category but it doesn't carry the same quantitative meaning as the
  release_year, since its more about order instead of an exact
  measurable gap.

- Continuous: Yes, for example the variable budget (which displays the
  amount of money, with decimals).

- Discrete: Yes, for example with the variable vote_count (which shows a
  variable that is countable, in this case the number of votes.)

3.  A movie studio wants to know which types of movies give maximal
    revenue. Perform the following steps to provide the movie studio
    with an analysis which corresponds to their request:

<!-- -->

a.  Summarize the variable revenue and report its mean, median, maximum,
    and minimum. \textbf{[2 points]}
b.  Which movie has the highest revenue in your data set and how much is
    this revenue. Which movie has the lowest and how much is its
    revenue? If multiple movies have the exact same highest or lowest
    revenue, give only one example. \textbf{[2 points]}
c.  Create a histogram of the variable revenue. Make sure it has an
    appropriate title, and appropriate titles and labels for the x- and
    y-axis. Describe the shape of the histogram. What does this tell you
    about the nature of making money in the movies industry?
    \textbf{[2 points]}
d.  Add a new variable to your data set: the log of revenue. When
    creating this variable, what happens to movies for which revenue is
    zero? What then happens when you calculate the mean of log revenue?
    \textbf{[2 points]}
e.  For movies that have a revenue of zero, replace log of revenue with
    "NA". What is now the mean of log of revenue? Create a histogram for
    log revenue, again with an appropriate title, x- and y-axis labels.
    Describe the shape of this histogram. \textbf{[2 points]}
f.  For the variables revenue and log of revenue calculate their
    skewness and kurtosis. How do these numbers relate to the shape of
    the histograms that you estimated under d.) and e.)?
    \textbf{[2 points]}

For each step, you should provide first all the code you used to answer
the question and then formulate an answer using full sentences.

Each week consists of 1, 2, or 3 subquestions. The total amount of
points you can earn per week is 20 points.

*Step a*

```{r}

#WRITE YOUR CODE HERE
summary(movies$revenue)
mean(movies$revenue)
median(movies$revenue)
max(movies$revenue)
min(movies$revenue)

```

**Your Answer:** The mean of revenue is \$82,727,885 and the median of
revenue is \$14,560,504. The maximum revenue is \$1,519,557,910 and the
minimum revenue is \$0

*Step b*

```{r}

#WRITE YOUR CODE HERE
##highest revenue 
movies[which.max(movies$revenue), c("title", "revenue")]
##lowest revenue
movies[which.min(movies$revenue), c("title","revenue")]

```

**Your Answer:** The movie which has the highest revenue is "The
Avengers" with a revenue of \$1,519,557,910. The movie with the lowest
revenue is "The Oogieloves in the Big Balloon Adventure" which has a
revenue of \$0.

*Step c*

```{r}

#WRITE YOUR CODE HERE
hist(movies$revenue, 
     main= "Movie Revenue",
     xlab= "Revenue (in dollars)", 
     ylab= "Frequency",
     col="hotpink")
```

**Your Answer:** The revenue data is mostly right-skewed since most
movies have a low revenue and only a few have a extremely high revenue.
This is shown in the histogram with a large bar at the start and which
thins out to just a couple movies at the end of the graph. The graph
suggests that the revenue is unevenly distributed in the film industry
with a big portion of movies earning way less than the big movies, and
needing a hit to earn a lot of revenue.

*Step d*

```{r}

#WRITE YOUR CODE HERE
movies$log_revenue <-log(movies$revenue)

##movies with revenue 0
sum(movies$revenue==0)
mean(movies$log_revenue)
```

**Your Answer:** There are 257 movies with a revenue of 0. R gives -Inf
as a response since the logarithm of 0 is undefined and approaching a
negative infinity. This causes the entire mean to become -Inf because of
the presence of these -Inf values (and making it not interpretative).

*Step e*

```{r}

#WRITE YOUR CODE HERE
movies$log_revenue[movies$revenue==0] <- NA
mean(movies$log_revenue, na.rm=TRUE)

hist(movies$log_revenue,
     main= "Log Revenue",
     xlab= "Log (Revenue)",
     ylab= "Frequency", 
     col= "hotpink")


```

**Your Answer:** The mean of the log revenue is now 17.28, after
replacing the movies with zero revenue with NA and excluding these from
the calculation with na.rm=TRUE. The histogram of the log revenue shows
a more symmetric bell shaped distribution in contrast to the more right
skewed histogram from step c. Most values are now concentrated around
the mean indicating that the log-transformation reduced the extreme
skewness.

*Step f*

```{r}

#WRITE YOUR CODE HERE
#to run this code: install.packages("moments")
library(moments)
skewness(movies$revenue)
kurtosis(movies$revenue)

skewness(movies$log_revenue, na.rm=TRUE)
kurtosis(movies$log_revenue, na.rm=TRUE)
```

**Your Answer:**

Revenue has a skewness of 3.90 and a kurtosis of 22.38. Both numbers are
higher than expected under a normal distribution (skewness=0, kurtosis ≈
3), which matches the histogram from step c (most movies earn relatively
little, while a couple movies earn far more). This pulls the
distribution far to the right and creates a long tail and extreme
outliers.

However, after the log-transformation the skewness drops to -1.95 and
the kurtosis to 10.95 which is far closer to the normal distribution
values. This fits the more symmetric histogram from step e. So the log
transformation reduced the skewness and kurtosis while still not being
perfectly normal, since the skewness is now slightly negative instead of
zero and the kurtosis remains above 3.

# Week 2

1 Is your dataset movies4.tsv the full population, or is it a sample of
a larger population? If the latter, how would you describe the full
population? \textbf{[4 points]}

*Your answer here:*

This data set is a sample of a larger population, not the full
population because the set only contains 808 movies which are not all of
the movies which are produced in history. The full population would be
more like all commercially released films, mostly English from 1990 to
2016, from which data is available.

2 For this question, you will assume that your data set is the full
population.

a.  What is the mean of the variable vote_average in your data set?
    \textbf{[2 points]}
b.  Create a new data set, called movies_sample. Make sure that it is a
    random sample of your data set of 25 movies. What is the mean of
    vote_average in this random sample? How does it compare to the mean
    of vote_average in 2a? \textbf{[2 points]}
c.  In a for loop, create 100 different samples of 25 movies, as in b,
    and estimate the mean within each sample. Save the mean of each
    sample in a vector called sample_means. So the first position of the
    vector would have the mean of the first sample, the second position
    the mean of the second sample, etc. Print the start of this vector.
    \textbf{[2 points]}
d.  Summarize and make a histogram of sample_means. What is the mean,
    standard deviation and shape of its distribution?
    \textbf{[2 points]}
e.  Using the formulas of the *Central Limit Theorem*, give the
    distribution of the sample mean of vote_average in a sample of 25
    movies from your population (including its expected value and
    standard deviation). How do these values compare to your answers at
    d.)? \textbf{[2 points]}

*Step a*

```{r}
#WRITE YOUR CODE HERE
mean(movies$vote_average)
```

**Your Answer:**

Assuming that the data set represents the full population, the
population mean of vote_average is 6.04.

*Step b*

```{r}
#WRITE YOUR CODE HERE
##fixes random number generator, makes the sample reproducible
set.seed(123)
movies_sample <-movies[sample(nrow(movies),25),]
mean(movies_sample$vote_average)
```

**Your Answer:** A random sample of 25 was drawn with the mean of 6.016
for the vote_average. This is very close to the population mean from
step a. The difference of 0.024 reflects the normal sampling variability
and wont match the true population mean but will be quite representative
for such a small sample.

*Step c*

```{r}
#WRITE YOUR CODE HERE
##fixes random generator, makes the sample reproducible 
set.seed(123)

sample_means <-numeric(100)

for (i in 1:100){
  temp_sample <-movies[sample(nrow(movies),25), ]
  sample_means[i] <- mean(temp_sample$vote_average)
}
head(sample_means)
```

**Your Answer:** With a loop was used to draw 100 samples of 25 movies
each and the mean of vote_average was calculated and stored for each
sample of the sample_means. The first six values of this vector are
6.016, 6.172,5.856,6.112, 6.016, 5.696.

*Step d*

```{r}
#WRITE YOUR CODE HERE
summary(sample_means)
mean(sample_means)
sd(sample_means)

hist(sample_means,
     main = "Sample Means", 
     xlab = "Sample Mean of vote_average",
     ylab = "Frequency",
     col = "hotpink")

```

**Your Answer:** The mean of sample_mean is 6.046, which is close to the
population mean of vote_average (6.04) found in step a. The standard
deviation of sample_means is 0.221, representing the standard error of
the sampling distribution. The histogram of sample_means shows an
approximately symmetric distribution centered around the population
mean.This is consistent with the Central Limit Theorem, which says that
the distribution of the sample means becomes more normal as the number
of samples increases, even when the underlying variable itself is not
perfectly normally distributed.

*Step e*

3.  Is there a variable in your data set which you would expect to
    follow a discrete uniform distribution? Explain, without looking at
    the data, why you expect this data to be discrete uniform. If the
    data would indeed follow a discrete uniform distribution, what would
    you expect the mean and standard deviation of this variable to be?
    Next, plot a histogram of the variable, and plot an appropriate
    discrete uniform distribution on top of this histogram. Comment
    whether the variable indeed follows this expected distribution. If
    the distribution deviates from the discrete uniform distribution,
    explain why this is the case. \textbf{[6 points]}

**Your Answer:**

```{r}
#WRITE YOUR CODE HERE
population_mean <-mean(movies$vote_average)
population_sd <- sd(movies$vote_average)

n<-25 
expected_value <- population_mean
standard_error <-population_sd/ sqrt(n)

expected_value
standard_error
```

**Your Answer:**

According to the Central Limit Theorem, the sampling distribution of the
mean of vote_average for samples of size 25 is around normal (with
expected value to the equal population mean (6.039) and a standard
deviation (0.237) close to the results found in d (6.046 and 0.221).The
small differences can be explained by the number of samples (100 in
comparison with infinite number of samples). With more simulated
samples, the empirical values would be expected to become even closer to
the theoretical CLT predictions.

# Week 3

For the next part of the assignment, assume that the movies in your data
frame are a random sample of a larger population of movies.

1.  Give a 90 percent confidence interval for the variable *revenue*.
    Interpret the result. \textbf{[2 points]}

```{r}
#WRITE YOUR CODE HERE

t.test(movies$revenue, conf.level=0.90)
```

**Your Answer:**

The 90% confidence interval for the mean of revenue is [\$72,731,406 ,
\$92,724,364]. This means that samples of this size (n=808) are drawn
repeatedly and for every time a confidence interval is drawn, it would
be expected that 90% of these intervals contain the true population mean
of revenue. Based on this sample that's drawn, it can be said with a 90%
confidence that the true population mean revenue lies between
\$72,731,406 and \$92,724,364.

2

a.  How many movies in your sample were directed by a male director? How
    many by a female director? \textbf{[2 points]}
b.  Test the null hypothesis that the chance that a movie is being
    directed by a male or female director is equal. Clearly state your
    null hypothesis and alternative hypothesis, and your chosen
    significance level. Use an appropriate R function to test your
    hypothesis, and state your conclusion. Also give the p-value that
    corresponds to your test statistic. \textbf{[2 points]}
c.  Recode revenue such that it is measured in millions of dollars. What
    is the variance of revenue for movies with a male director? What is
    the variance of revenue for movies with a female director?
    \textbf{[2 points]}
d.  Assume that the variance of revenue for movies with a male director
    in your data is the same as the variance for movies with a male
    director in your population (that is, there is no sampling
    uncertainty in this estimate). Now, set up a hypothesis test to test
    for the null hypothesis that the variance of revenue for movies with
    a female director is equal to the variance for movies with a male
    director. Clearly state your null hypothesis and alternative
    hypothesis, and your chosen significance level. Calculate your test
    statistic and tell how your test statistic is distributed, and state
    your conclusion. Also give the p-value that corresponds to your test
    statistic. \textbf{[2 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE
table(movies$director_gender)

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE
table_gender<-table(movies$director_gender)
print(table_gender)
class(table_gender)

prop.test(x=table_gender["male"], n=sum(table_gender),p=0.5)
```

**Your Answer:**

The null hypothesis (H0): The probability that a movie is directed by a male director is equal (so 0.5).

alternative hypothesis (H1): the probability that a movie is directed by a male director is not equal to 0.5.

significance level=0.5

This hypothesis was tested with a one-sample proportions test. This sample consisted of 765 movies(with a known director gender), where 685 movies are directed by a male director.This gives a sample proportion of 0.895 and yields a statistic of X-squared of 476.88 with a p-value< 2.2e-16 with a 95% confidence interval of [0.871, 0.916]. Since the p-value is smaller than the significance level of 0.05 the null hypothesis is rejected.This provides strong evidence that the probability of a movie being directed by a male director is equal to 0.5 and that the data suggest that male directors are more common than female directors in this data set.

*step c*

```{r}
movies$revenue_m <- movies$revenue / 1e6
var_male <- var(movies$revenue_m[movies$director_gender == "male"], na.rm = TRUE)
var_female <- var(movies$revenue_m[movies$director_gender == "female"], na.rm = TRUE)
var_male ; var_female
```

**Your Answer:**

Write your formulated response here.

*step d*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**
To test whether the variance of revenue differs between movies with a female director and movies with a male director, I created the following hypothesis test. Firstly, I did a Null hypothesis: variance of revenue for movies with female director = variance of revenue for movies with male 

Write your formulated response here.

3

a.  Create a scatter plot with year on the x axis and mean of revenue
    within that year on the y-axis. Make sure it has an appropriate
    title, and appropriate titles and labels for the x- and y-axis. Is
    revenue of movies increasing or decreasing over time?
    \textbf{[3 points]}
b.  Recreate the scatter plot with year on the x axis and mean_revenue
    on the y-axis, but now add bars around each point, indicating the
    95% confidence interval. \textbf{[3 points]}
c.  If you look closely at the resulting plot in b.), you will probably
    see that the confidence intervals in some years are wider than in
    other years. What are some possible reasons that a confidence
    interval in a given year can be wide? Can you verify this using your
    data? \textbf{[4 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE
revenue_by_year <-aggregate(revenue~ release_year, data=movies,FUN=mean)

head(revenue_by_year)

plot(revenue_by_year$release_year, revenue_by_year$revenue,
     main= "Mean Movie revenue by release year",
     xlab= "Release year",
     ylab="Mean revenue (in dollars)",
     pch=19,
     col= "hotpink")
```

**Your Answer:**
A scatter plot was created showing the mean revenue per release year and the plot does not show a clear consistent trend of increasing or decreasing over time but fluctuates up and down from year to year. Some of the highest average revenue occur around the 1990s and around 2015 in the dataset, while many of the years in between show lower and more similair average revenues. This shows that the average revenues has not clearly increased over time, and yearly averages appear to be more strongly influenced by a small number of high-or low revenue movies from that specifical year than a general industry wide trend. 

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step c*

```{r}
#WRITE YOUR CODE HERE

```

# Week 4

1.  There is an argument going on in the movie studio. *Bob* claims that
    production budgets are getting out of hand, and that the studio
    should focus on making cheaper movies. *Chantal* disagrees. She
    tells Bob that \`\`Every dollar we spend on movie production is more
    than offset by the increase in movie revenue''.

<!-- -->

a.  Set up a regression model to test Chantal's claim, and estimate it.
    That is, estimate:
    $$\text{Revenue}_i=\beta_0+\beta_1 \text{Budget}_i +\varepsilon_i.$$
    Print a summary of your estimated model. \textbf{[2 points]}
b.  What is the estimated value of $\beta_1$ and how do you interpet it?
    \textbf{[2 points]}
c.  Test for the null hypothesis that $\beta_1 \leq 1$. Report the
    p-value and state your conclusion. \textbf{[2 points]}
d.  Next, estimate the model
    $$\text{Log Revenue}_i=\beta_0+\beta_1 \text{Log Budget}_i +\varepsilon_i.$$
    When creating the variables Log Revenue and Log Budget, make sure
    that movies with a Revenue or Budget of zero are assigned the value
    "NA". Print a summary of your estimated model. \textbf{[2 points]}
e.  What is the estimated value of $\beta_1$ and how do you interpet it?
    \textbf{[2 points]}
f.  Which model has better fit? The level-level model or the log-log
    model? Explain. \textbf{[2 points]}
g.  Who do you think is correct? Bob or Chantal? What would you advise
    the movie studio to do? \textbf{[2 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step c*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step d*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step e*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step f*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step g*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

2

a.  Make a scatterplot with log revenue on the y-axis, and log budget on
    the x-axis. Within the same scatterplot, draw a straight line which
    summarizes the association between the log of revenue and log of
    budget. \textbf{[3 points]}
b.  Using the insights from the scatterplot, your linear model, and your
    data, find an example of a movie that vastly overperformed. That
    means, find a movie that had much more revenue than expected, given
    its budget. For this movie, report its log of revenue, its predicted
    log of revenue, and its residual. \textbf{[3 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

# Week 5

a.  Make a frequency table of the variable genre. Which are the three
    genres that occur the most? \textbf{[2 points]}
b.  Create a new variable called genre2. Make sure that the three most
    popular genres remain the same, but that all the other genres get
    categorized into one genre called “Other”. Report a frequency table
    of this new variable genre2. \textbf{[2 points]}
c.  Estimate an OLS model which has as dependent variable the log of
    revenue of a movie, and as independent variable the log of budget, a
    dummy for each level that genre2 can take, and the year of release.
    Show a summary of the resulting model and interpret each
    coefficient. \textbf{[4 points]}

The movie studio that you work at is releasing a new movie in 2026. It
will be a Drama movie with a budget of 20,000,0000. It will have a
runtime of 120 minutes.

d.  Estimate a model that is able to predict the revenue of this movie.
    Give its predicted revenue and include a 90% prediction interval.
    \textbf{[5 points]}
e.  Plot the residuals against various independent variables in the
    model. Do you find any evidence of heteroskedasticity?
    \textbf{[2 points]}
f.  One executive at the studio wants to time the release of the movie
    to a specific month of the year such that they can maximize revenue.
    Another executive is of the opinion that the month in which the
    movie is released will not have a big impact on its revenue.
    Estimate a model that can test whether the month of release impacts
    the revenue of a movie. Use an appropriate hypothesis test to test
    whether month of release matters. What would you advise the movie
    studio regarding the timing of the release of the movie?
    \textbf{[5 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step c*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step d*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step e*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step f*

```{r}
#WRITE YOUR CODE HERE

```
