---
title: "QRM II Graded Assignment (6)"
subtitle: "Period 1, 2026"
author: "Sophie Thoolen, Clemence van Gils, Benthe Tromp en Roos Bakker "
date:  "`r format(Sys.Date(), '%d-%m-%Y')`"
output:
  html_document:
    df_print: paged
  pdf_document:
    number_sections: true

header-includes:
- "\\setcounter{section}{-1}"
- |
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{
    showspaces = false,
    showtabs = false,
    breaklines,
    commandchars=\\\{\}
format:
  html:
    code-overflow: wrap
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 5,fig.height = 3.5)
```

# Introduction

This assignment is to be completed in groups of 4-5. Further, all
students in your group need to be assigned to the same R tutorial group
(Friday's tutorial). You can sign yourself up for a group on Canvas.
Please do so
\textbf{before the start of your first R tutorial on Friday September 4th.}
You can use the Discussion Board in Canvas if you do not have a group
yet or if your group is incomplete.

The assignment has 5 parts, and each part corresponds to the course
material of that week (with the exclusion of week 6, for which there is
no R programming material).

You are supposed to hand in these assignments on Canvas at the following
dates:

- **Deadline 1** *Sunday September 27th, at 23:59pm*: you are supposed
  to hand in weeks 1, 2, and 3 of this assignment. This will determine
  18% of your overall course grade
- **Deadline 2** *Sunday October 11th, at 23:59pm*: you are supposed to
  hand in weeks 4, and 5 of this assignment. This will determine 12% of
  your overall course grade

The R tutorials (each Friday) will consist of two halves. During the
first half, you will discuss the tutorial exercises. These can be
downloaded separately from Canvas. During the second half, you can work
on this graded assignment within your own group. The purpose is that you
find out how to work with R for doing statistical analyses by yourself.
The tutorial exercises are meant to teach you basic commands to get you
started, but to answer the problem sets in this assignment, you might
need to research your own solutions, and use functions and commands not
described in the tutorial exercises. Learning how to solve your own
research problems is integral part of learning R. When you and your
group get stuck on how to approach an exercise, the hierarchy in finding
your way is as follows:

- use the concepts from the tutorial exercises;
- use the cheat sheets available on Canvas;
- use Google, YouTube, StackOverflow, or another website;
- ask the teacher.

The use of generative AI is \textbf{not} permitted and may result in a
grade of 0. See the AI protocol in the course manual for details.

To answer the assignment, you can simply fill out this R markdown
document. There are designated places which you can fill with R code.
There are also designated spaces for you to answer each question. Often,
the structure of an answer will be as follows. First, you type the R
code in the designated box. This will show how you analyzed the data to
get the answer to the question. Below the box for the R code, you will
then summarize your answer to the question, i.e. what are the
conclusions that you draw from the data analysis?

When handing in, you are supposed to submit this .Rmd file, and a
knitted version of this document. You can knit this document to pdf,
word, or html. Knitting to pdf requires you to have a .tex distribution
installed on your computer. Knitting to Word requires you to have Word
installed.

The exercises are designed such that you should be able to finish the
majority of them during the tutorial each week. If you are not able to
finish them fully during that time, you are expected to work on it in
your own time using the computers on campus or your own device. It is
best to meet as a group in-person when working together. If you want to
work remotely, github is a good platform to guarantee smooth
collaboration. Alternatively, you can email this .Rmd file back and
forth to one another as a group, but this is not recommended as it is
more cumbersome.

We encourage you to keep your code blocks, printing statements, and
final answers, as short as possible. In any case, there is a page limit
of 6 pages per week, which encompasses the total length of this document
which consists of the questions, your coding lines, and your answers.
When your answers to questions of the respective week exceed this page
limit, they will not be graded, resulting in zero points.

# Week 1

1.  Find the dataset “movies4.tsv” on Canvas. Describe your data set:
    How many observations does it have. How many variables are there?
    How many subjects? What consists of a subject? \textbf{[4 points]}

```{r}
#WRITE YOUR CODE HERE
movies <- read.delim("movies4.tsv", sep = "\t", header = TRUE)

#number observations
nrow(movies)
#number of variables 
ncol(movies)

head(movies)
str(movies)
summary (movies)

#number of subjects 
nrow(movies)
##checked if all observations are different
length(unique(movies$title))

```

**Your Answer:**

The data set contains 808 observations and 19 variables. A subject is a
individual movie and each observation corresponds to a movie, identified
by the variable 'title'. Since there is no recurrence of the same movie
name, the number of subjects is equal to the number of observations.
(which is 808)

2.  Which of the following types of variables are present in your data
    set? (i) nominal; (ii) ordinal; (iii); continuous; (iv) discrete. If
    present, name one example of such a variable present in your data
    set. \textbf{[4 points]}

```{r answer 2}
#WRITE YOUR CODE HERE
##checking the variables
str(movies)
```

**Your Answer:**

The following types of variables are present in this data set:

- Nominal: Yes, for example the variable genre or language which are
  organized by category without a specific order.

- Ordinal: Yes, for example the variable release_month (stored as a
  number but represents a month). This gives it a way to be ordered by
  category but it doesn't carry the same quantitative meaning as the
  release_year, since its more about order instead of an exact
  measurable gap.

- Continuous: Yes, for example the variable budget (which displays the
  amount of money, with decimals).

- Discrete: Yes, for example with the variable vote_count (which shows a
  variable that is countable, in this case the number of votes.)

3.  A movie studio wants to know which types of movies give maximal
    revenue. Perform the following steps to provide the movie studio
    with an analysis which corresponds to their request:

<!-- -->

a.  Summarize the variable revenue and report its mean, median, maximum,
    and minimum. \textbf{[2 points]}
b.  Which movie has the highest revenue in your data set and how much is
    this revenue. Which movie has the lowest and how much is its
    revenue? If multiple movies have the exact same highest or lowest
    revenue, give only one example. \textbf{[2 points]}
c.  Create a histogram of the variable revenue. Make sure it has an
    appropriate title, and appropriate titles and labels for the x- and
    y-axis. Describe the shape of the histogram. What does this tell you
    about the nature of making money in the movies industry?
    \textbf{[2 points]}
d.  Add a new variable to your data set: the log of revenue. When
    creating this variable, what happens to movies for which revenue is
    zero? What then happens when you calculate the mean of log revenue?
    \textbf{[2 points]}
e.  For movies that have a revenue of zero, replace log of revenue with
    "NA". What is now the mean of log of revenue? Create a histogram for
    log revenue, again with an appropriate title, x- and y-axis labels.
    Describe the shape of this histogram. \textbf{[2 points]}
f.  For the variables revenue and log of revenue calculate their
    skewness and kurtosis. How do these numbers relate to the shape of
    the histograms that you estimated under d.) and e.)?
    \textbf{[2 points]}

For each step, you should provide first all the code you used to answer
the question and then formulate an answer using full sentences.

Each week consists of 1, 2, or 3 subquestions. The total amount of
points you can earn per week is 20 points.

*Step a*

```{r}

#WRITE YOUR CODE HERE
summary(movies$revenue)
mean(movies$revenue)
median(movies$revenue)
max(movies$revenue)
min(movies$revenue)

```

**Your Answer:** The mean of revenue is \$82,727,885 and the median of
revenue is \$14,560,504. The maximum revenue is \$1,519,557,910 and the
minimum revenue is \$0

*Step b*

```{r}

#WRITE YOUR CODE HERE
##highest revenue 
movies[which.max(movies$revenue), c("title", "revenue")]
##lowest revenue
movies[which.min(movies$revenue), c("title","revenue")]

```

**Your Answer:** The movie which has the highest revenue is "The
Avengers" with a revenue of \$1,519,557,910. The movie with the lowest
revenue is "The Oogieloves in the Big Balloon Adventure" which has a
revenue of \$0.

*Step c*

```{r}

#WRITE YOUR CODE HERE
hist(movies$revenue, 
     main= "Movie Revenue",
     xlab= "Revenue (in dollars)", 
     ylab= "Frequency",
     col="hotpink")
```

**Your Answer:** The revenue data is mostly right-skewed since most
movies have a low revenue and only a few have a extremely high revenue.
This is shown in the histogram with a large bar at the start and which
thins out to just a couple movies at the end of the graph. The graph
suggests that the revenue is unevenly distributed in the film industry
with a big portion of movies earning way less than the big movies, and
needing a hit to earn a lot of revenue.

*Step d*

```{r}

#WRITE YOUR CODE HERE
movies$log_revenue <-log(movies$revenue)

##movies with revenue 0
sum(movies$revenue==0)
mean(movies$log_revenue)
```

**Your Answer:** There are 257 movies with a revenue of 0. R gives -Inf
as a response since the logarithm of 0 is undefined and approaching a
negative infinity. This causes the entire mean to become -Inf because of
the presence of these -Inf values (and making it not interpretative).

*Step e*

```{r}

#WRITE YOUR CODE HERE
movies$log_revenue[movies$revenue==0] <- NA
mean(movies$log_revenue, na.rm=TRUE)

hist(movies$log_revenue,
     main= "Log Revenue",
     xlab= "Log (Revenue)",
     ylab= "Frequency", 
     col= "hotpink")


```

**Your Answer:** The mean of the log revenue is now 17.28, after
replacing the movies with zero revenue with NA and excluding these from
the calculation with na.rm=TRUE. The histogram of the log revenue shows
a more symmetric bell shaped distribution in contrast to the more right
skewed histogram from step c. Most values are now concentrated around
the mean indicating that the log-transformation reduced the extreme
skewness.

*Step f*

```{r}

#WRITE YOUR CODE HERE
#to run this code: install.packages("moments")
library(moments)
skewness(movies$revenue)
kurtosis(movies$revenue)

skewness(movies$log_revenue, na.rm=TRUE)
kurtosis(movies$log_revenue, na.rm=TRUE)
```

**Your Answer:**

Revenue has a skewness of 3.90 and a kurtosis of 22.38. Both numbers are
higher than expected under a normal distribution (skewness=0, kurtosis ≈
3), which matches the histogram from step c (most movies earn relatively
little, while a couple movies earn far more). This pulls the
distribution far to the right and creates a long tail and extreme
outliers.

However, after the log-transformation the skewness drops to -1.95 and
the kurtosis to 10.95 which is far closer to the normal distribution
values. This fits the more symmetric histogram from step e. So the log
transformation reduced the skewness and kurtosis while still not being
perfectly normal, since the skewness is now slightly negative instead of
zero and the kurtosis remains above 3.

# Week 2

1 Is your dataset movies4.tsv the full population, or is it a sample of
a larger population? If the latter, how would you describe the full
population? \textbf{[4 points]}

*Your answer here:*

This data set is a sample of a larger population, not the full
population because the set only contains 808 movies which are not all of
the movies which are produced in history. The full population would be
more like all commercially released films, mostly English from 1990 to
2016, from which data is available.

2 For this question, you will assume that your data set is the full
population.

a.  What is the mean of the variable vote_average in your data set?
    \textbf{[2 points]}
b.  Create a new data set, called movies_sample. Make sure that it is a
    random sample of your data set of 25 movies. What is the mean of
    vote_average in this random sample? How does it compare to the mean
    of vote_average in 2a? \textbf{[2 points]}
c.  In a for loop, create 100 different samples of 25 movies, as in b,
    and estimate the mean within each sample. Save the mean of each
    sample in a vector called sample_means. So the first position of the
    vector would have the mean of the first sample, the second position
    the mean of the second sample, etc. Print the start of this vector.
    \textbf{[2 points]}
d.  Summarize and make a histogram of sample_means. What is the mean,
    standard deviation and shape of its distribution?
    \textbf{[2 points]}
e.  Using the formulas of the *Central Limit Theorem*, give the
    distribution of the sample mean of vote_average in a sample of 25
    movies from your population (including its expected value and
    standard deviation). How do these values compare to your answers at
    d.)? \textbf{[2 points]}

*Step a*

```{r}
#WRITE YOUR CODE HERE
mean(movies$vote_average)
```

**Your Answer:**

Assuming that the data set represents the full population, the
population mean of vote_average is 6.04.

*Step b*

```{r}
#WRITE YOUR CODE HERE
##fixes random number generator, makes the sample reproducible
set.seed(123)
movies_sample <-movies[sample(nrow(movies),25),]
mean(movies_sample$vote_average)
```

**Your Answer:** A random sample of 25 was drawn with the mean of 6.016
for the vote_average. This is very close to the population mean from
step a. The difference of 0.024 reflects the normal sampling variability
and wont match the true population mean but will be quite representative
for such a small sample.

*Step c*

```{r}
#WRITE YOUR CODE HERE
##fixes random generator, makes the sample reproducible 
set.seed(123)

sample_means <-numeric(100)

for (i in 1:100){
  temp_sample <-movies[sample(nrow(movies),25), ]
  sample_means[i] <- mean(temp_sample$vote_average)
}
head(sample_means)
```

**Your Answer:** With a loop was used to draw 100 samples of 25 movies
each and the mean of vote_average was calculated and stored for each
sample of the sample_means. The first six values of this vector are
6.016, 6.172,5.856,6.112, 6.016, 5.696.

*Step d*

```{r}
#WRITE YOUR CODE HERE
summary(sample_means)
mean(sample_means)
sd(sample_means)

hist(sample_means,
     main = "Sample Means", 
     xlab = "Sample Mean of vote_average",
     ylab = "Frequency",
     col = "hotpink")

```

**Your Answer:** The mean of sample_mean is 6.046, which is close to the
population mean of vote_average (6.04) found in step a. The standard
deviation of sample_means is 0.221, representing the standard error of
the sampling distribution. The histogram of sample_means shows an
approximately symmetric distribution centered around the population
mean.This is consistent with the Central Limit Theorem, which says that
the distribution of the sample means becomes more normal as the number
of samples increases, even when the underlying variable itself is not
perfectly normally distributed.

*Step e*

```{r}
#WRITE YOUR CODE HERE
population_mean <-mean(movies$vote_average)
population_sd <- sd(movies$vote_average)

n<-25 
expected_value <- population_mean
standard_error <-population_sd/ sqrt(n)

expected_value
standard_error
```

**Your Answer:**

According to the Central Limit Theorem, the sampling distribution of the
mean of vote_average for samples of size 25 is around normal (with
expected value to the equal population mean (6.039) and a standard
deviation (0.237) close to the results found in d (6.046 and 0.221).The
small differences can be explained by the number of samples (100 in
comparison with infinite number of samples). With more simulated
samples, the empirical values would be expected to become even closer to
the theoretical CLT predictions.

3.  Is there a variable in your data set which you would expect to
    follow a discrete uniform distribution? Explain, without looking at
    the data, why you expect this data to be discrete uniform. If the
    data would indeed follow a discrete uniform distribution, what would
    you expect the mean and standard deviation of this variable to be?
    Next, plot a histogram of the variable, and plot an appropriate
    discrete uniform distribution on top of this histogram. Comment
    whether the variable indeed follows this expected distribution. If
    the distribution deviates from the discrete uniform distribution,
    explain why this is the case. \textbf{[6 points]}

    ```{r}
    # theoretical values
    n <- 31
    a <- 1
    b <- 31
    exp_mean <- (a+b) / 2
    exp_sd <- sqrt((n^2 - 1) / 12)

    exp_mean # 16
    exp_sd # 8.94

    # true mean and standard deviation in the data
    mean(movies$release_day,na.rm = TRUE)
    sd(movies$release_day,na.rm = TRUE) 

    #histogram with discrete uniform overlay
    hist(movies$release_day,
         main= "Release Day with discrete uniform overlay",
         xlab= "Day of the month",
         ylab= "Frequency",
         col="pink",
         breaks= 31)

    expected_freq <- sum(!is.na(movies$release_day))/31
    abline(h=expected_freq,col="blue",lwd=2,lty=2)

    ```

**Your Answer:**

We would expect that the variable release_day follows a discrete uniform
distribution. Based on factors (such as season and holiday periods) film
studios choose a release date, but there is no reason to assume that a
specific date in the month makes a real difference (for example the 18th
compared to the 19th). So movies are relatively evenly spread across the
days.

If release_day is uniform over 1-31, the expected mean would be
(1+31)/2=16, and the expected sd sqrt(31\^2 -1)/12 ≈ 8.94. The actual
mean and sd are actually very close to these theoretical values (15.33
and 8.56).

However the histogram shows that it is not perfectly uniform, for
example day 1 has big spike (61 movies) as well as day 15 and 25 which
stand out above the blue line. There also seems to be a decline from day
27 to 31, but that's not a real deviation since not all months have
those days. Only the spikes at day 1, 15 and 25 can be considered as
real deviation. Studios likely release movies on more memorable 'round'
dates for marketing reasons than just spreading release dates randomly.
It looks more like a choice, not a random date, while still matching the
overall mean and sd from the uniform prediction.

# Week 3

For the next part of the assignment, assume that the movies in your data
frame are a random sample of a larger population of movies.

1.  Give a 90 percent confidence interval for the variable *revenue*.
    Interpret the result. \textbf{[2 points]}

```{r}
#WRITE YOUR CODE HERE

t.test(movies$revenue, conf.level=0.90)
```

**Your Answer:**

The 90% confidence interval for the mean of revenue is [\$72,731,406 ,
\$92,724,364]. This means that samples of this size (n=808) are drawn
repeatedly and for every time a confidence interval is drawn, it would
be expected that 90% of these intervals contain the true population mean
of revenue. Based on this sample that's drawn, it can be said with a 90%
confidence that the true population mean revenue lies between
\$72,731,406 and \$92,724,364.

2

a.  How many movies in your sample were directed by a male director? How
    many by a female director? \textbf{[2 points]}
b.  Test the null hypothesis that the chance that a movie is being
    directed by a male or female director is equal. Clearly state your
    null hypothesis and alternative hypothesis, and your chosen
    significance level. Use an appropriate R function to test your
    hypothesis, and state your conclusion. Also give the p-value that
    corresponds to your test statistic. \textbf{[2 points]}
c.  Recode revenue such that it is measured in millions of dollars. What
    is the variance of revenue for movies with a male director? What is
    the variance of revenue for movies with a female director?
    \textbf{[2 points]}
d.  Assume that the variance of revenue for movies with a male director
    in your data is the same as the variance for movies with a male
    director in your population (that is, there is no sampling
    uncertainty in this estimate). Now, set up a hypothesis test to test
    for the null hypothesis that the variance of revenue for movies with
    a female director is equal to the variance for movies with a male
    director. Clearly state your null hypothesis and alternative
    hypothesis, and your chosen significance level. Calculate your test
    statistic and tell how your test statistic is distributed, and state
    your conclusion. Also give the p-value that corresponds to your test
    statistic. \textbf{[2 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE
table(movies$director_gender)

```

**Your Answer:**

This code counts how many times each value (male and female) appears in
the director_gender column. The result shows 80 movies with a female
director and 685 movies with a male director.

*step b*

```{r}
#WRITE YOUR CODE HERE
table_gender<-table(movies$director_gender)
print(table_gender)
class(table_gender)

prop.test(x=table_gender["male"], n=sum(table_gender),p=0.5)
```

**Your Answer:**

The null hypothesis (H0): The probability that a movie is directed by a
male director is equal (so 0.5).

alternative hypothesis (H1): the probability that a movie is directed by
a male director is not equal to 0.5.

significance level=0.05

This hypothesis was tested with a one-sample proportions test. This
sample consisted of 765 movies(with a known director gender), where 685
movies are directed by a male director.This gives a sample proportion of
0.895 and yields a statistic of X-squared of 476.88 with a p-value\<
2.2e-16 with a 95% confidence interval of [0.871, 0.916]. Since the
p-value is smaller than the significance level of 0.05 the null
hypothesis is rejected.This provides strong evidence that the
probability of a movie being directed by a male director is not equal to
0.5 and that male directors are more common.

*step c*

```{r}
movies$revenue_m <- movies$revenue / 1e6
var_male <- var(movies$revenue_m[movies$director_gender == "male"], na.rm = TRUE)
var_female <- var(movies$revenue_m[movies$director_gender == "female"], na.rm = TRUE)
var_male ; var_female
```

**Your Answer:**

The variance of revenue is in million of dollars. It is approximately
31,137.62 for movies with a director that is a male and approximately
13,224.54 for movies with a female director. The variance is larger for
movies with a male director.

*step d*

```{r}
#WRITE YOUR CODE HERE
revenue_female <- movies$revenue_m[which(movies$director_gender == "female")]
revenue_male   <- movies$revenue_m[which(movies$director_gender == "male")]

n_female <- length(revenue_female)
s2_female <- var(revenue_female)
sigma2_male <- var(revenue_male)

chi2_stat <- (n_female - 1) * s2_female / sigma2_male
df_f <- n_female - 1

p_value <- 2 * min(pchisq(chi2_stat, df_f), 1 - pchisq(chi2_stat, df_f))

chi2_stat
df_f
p_value
```

**Your Answer:**

This code splits revenue (in millions) into two groups based on director
gender and then calculates the sample size and variance for
female-directed movies and the variance for male-directed movies
(treated as a known, fixed value). After that, the chi-square test and
its degrees of freedom are calculated, and after that the two-sided
p-value is calculated. The result shows a test statistic of 33.55229
with 79 degrees of freedom and a p-value of 3.226983e-06. This p-value
is way smaller than the significance level of 0.05 which means that the
null hypothesis is rejected. The variance of revenue for female-directed
movies differs (is lower) from the variance for movies with a male
director.

3

a.  Create a scatter plot with year on the x axis and mean of revenue
    within that year on the y-axis. Make sure it has an appropriate
    title, and appropriate titles and labels for the x- and y-axis. Is
    revenue of movies increasing or decreasing over time?
    \textbf{[3 points]}
b.  Recreate the scatter plot with year on the x axis and mean_revenue
    on the y-axis, but now add bars around each point, indicating the95%
    confidence interval. \textbf{[3 points]}
c.  If you look closely at the resulting plot in b.), you will probably
    see that the confidence intervals in some years are wider than in
    other years. What are some possible reasons that a confidence
    interval in a given year can be wide? Can you verify this using your
    data? \textbf{[4 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE
revenue_by_year <-aggregate(revenue~ release_year, data=movies,FUN=mean)

head(revenue_by_year)

plot(revenue_by_year$release_year, revenue_by_year$revenue,
     main= "Mean Movie revenue by release year",
     xlab= "Release year",
     ylab="Mean revenue (in dollars)",
     pch=19,
     col= "hotpink")
```

**Your Answer:** A scatter plot was created showing the mean revenue per
release year and the plot does not show a clear consistent trend of
increasing or decreasing over time but fluctuates up and down from year
to year. Some of the highest average revenue occur around the 1990s and
around 2015 in the dataset, while many of the years in between show
lower and more similar average revenues. This shows that the average
revenues has not clearly increased over time, and yearly averages appear
to be more strongly influenced by a small number of high-or low revenue
movies from that specific year than a general industry wide trend.

*step b*

```{r}
#WRITE YOUR CODE HERE
mean_revenue <- aggregate(revenue ~ release_year, data=movies, FUN=mean)
sd_revenue <- aggregate(revenue ~ release_year, data=movies, FUN=sd)
n_revenue <- aggregate(revenue ~ release_year, data=movies, FUN=length)

se <- sd_revenue$revenue / sqrt(n_revenue$revenue)
lower <- mean_revenue$revenue - 1.96*se
upper <- mean_revenue$revenue + 1.96*se

plot(mean_revenue$release_year, mean_revenue$revenue,
main="Mean movie revenue by release year with 95% confidence interval",
     xlab="Release year",
     ylab="Mean revenue (in dollars)",
     pch=19,
     col="hotpink",
     cex.main=0.9,
     ylim=c(min(lower), max(upper)))

arrows(mean_revenue$release_year, lower,
       mean_revenue$release_year, upper,
       angle=90, code=3, length=0.05, col="hotpink")
```

**Your Answer:** In this scatter plot we create two extra steps on top
of our first scatter plot. We calculate the standard deviation and we
count the amount of movies per year (in addition to the mean) which lets
us calculate the standard error (how uncertain the mean is). After that,
we get the upper and lower bounds of the confidence interval, which you
can see in the scatter plot (with caps on both sides to make it more
clear).

*step c*

```{r}
#WRITE YOUR CODE HERE
verify <- data.frame(release_year = mean_revenue$release_year,
                      n = n_revenue$revenue,
                      sd = sd_revenue$revenue,
                      ci_width = upper - lower)
verify[order(-verify$ci_width), ]
```

This code creates a table which shows the number of movies, standard
deviation of revenue, and the width of the confidence interval for each
year, sorted from widest to narrowest. This makes it easy to check
whether the years with the widest intervals are also the years with a
small sample size and/or a large standard deviation. There are two main
reasons why confidence intervals can be wide in a specific year: 1)
Small sample size (this leads to a low n): if only a couple of movies
were released in a specific year, the mean is based on less data, which
makes it less reliable. This could lead to a wider confidence interval.
A good example for this reason is year 1990. In this year, n = 9
(relatively small sample size), with a very wide confidence interval:
244988199. This supports the idea that a small sample size leads to a
wider interval. 2) High variability in revenue (this leads to a high
sd): in a given year, movies can be hits or big flops. This leads to
revenue values which are spread far apart. This large spread could also
make the confidence interval wider. A good example for this reason is
year 2012. In this year, n = 51 (relatively large sample size), which
could lead to a small interval. However, the standard deviation is
309479166, and the confidence interval is still 169876145. This shows
that high variability in revenue can lead to a wide confidence interval
even though the sample size is big.

# Week 4

1.  There is an argument going on in the movie studio. *Bob* claims that
    production budgets are getting out of hand, and that the studio
    should focus on making cheaper movies. *Chantal* disagrees. She
    tells Bob that \`\`Every dollar we spend on movie production is more
    than offset by the increase in movie revenue''.

<!-- -->

a.  Set up a regression model to test Chantal's claim, and estimate it.
    That is, estimate:
    $$\text{Revenue}_i=\beta_0+\beta_1 \text{Budget}_i +\varepsilon_i.$$
    Print a summary of your estimated model. \textbf{[2 points]}
b.  What is the estimated value of $\beta_1$ and how do you interpet it?
    \textbf{[2 points]}
c.  Test for the null hypothesis that $\beta_1 \leq 1$. Report the
    p-value and state your conclusion. \textbf{[2 points]}
d.  Next, estimate the model
    $$\text{Log Revenue}_i=\beta_0+\beta_1 \text{Log Budget}_i +\varepsilon_i.$$
    When creating the variables Log Revenue and Log Budget, make sure
    that movies with a Revenue or Budget of zero are assigned the value
    "NA". Print a summary of your estimated model. \textbf{[2 points]}
e.  What is the estimated value of $\beta_1$ and how do you interpet it?
    \textbf{[2 points]}
f.  Which model has better fit? The level-level model or the log-log
    model? Explain. \textbf{[2 points]}
g.  Who do you think is correct? Bob or Chantal? What would you advise
    the movie studio to do? \textbf{[2 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE
model1<-lm(revenue ~ budget, data=movies)

summary(model1)
```

**Your Answer:**

We estimate the model
Revenue:$$\text{Revenue}_i=\beta_0+\beta_1 \text{Budget}_i +\varepsilon_i.$$

by OLS. The summary of the estimated model consists of the intercept of
-1.163e+07, the slope on budget=3.162 and R\^2=0.5994

*step b*

**Your Answer:**

The estimated value of β₁ (used from code a) is 3.162, where both
variables are measured in dollars. This means that a one-dollars
increase in a movie's budget is associated with an average increase in
revenue of \$3.16 dollars. The estimate is statistically significant
since t=34.73 and p\<0.001

*step c*

```{r}
#WRITE YOUR CODE HERE
b1 <- coef(summary(model1))["budget","Estimate"]
se <- coef(summary(model1))["budget", "Std. Error"]

# H0: beta1 <= 1
t_stat <-(b1-1)/se
t_stat

#one-sided p-value (right tail)
p_val <-pt(t_stat, df=df.residual(model1),lower.tail=FALSE)
p_val
```

**Your Answer:**

Since Chantal claims that every dollar that is spend on production is
more than offset by an increase in revenue, which means β₁\>1 we test:

H0: β₁\<=1

H1: β₁\> 1

The t-statistic is t=23.75 with 806 degrees of freedom. The one-sided
p-value is 3.28 x 10\^-95 which is very close to zero. That's why we
reject H0 since p\<0.05, because there is strong statistical evidence
that β₁ is larger than 1 and so the data supports Chantal's claim that
an extra dollar of budget is associated with more than one extra dollar
of revenue.

*step d*

```{r}
#WRITE YOUR CODE HERE
#making the log-variables 
movies$log_revenue <-ifelse(movies$revenue ==0, NA, log(movies$revenue))
movies$log_budget <- ifelse(movies$budget ==0, NA, log(movies$budget))

model2<-lm(log_revenue ~ log_budget, data=movies)

summary(model2)
```

**Your Answer:**

We created the variables log_revenue and log_budget, assigning NA to the
movies with a revenue or budget of zero. Plus we estimated the log-log
model by OLS. The summary of the estimated model is shown above (by
summary(model2))

*step e*

```{r}
#WRITE YOUR CODE HERE
##results used from code from d 
```

**Your Answer:**

The estimated value of β₁ is 1.030. This translates to β₁ being an
elasticity in a log-log model: a 1% increase in a movie's budget is
associated with an average increase in revenue of 1.03%. The estimate is
statistically significant since the t value is 22.52 and p\<0.001.

*step f*

```{r}
#WRITE YOUR CODE HERE
summary(model1)$r.squared
summary(model2)$r.squared 
```

**Your Answer:**

Based on R² alone, the level-level model seems to fit better (R^2^ of
0.599) than the log-log model (R^2^ of 0.495). However, these values
cannot be compared directly, for two reasons. First, the dependent
variables are different (revenue in dollars vs log revenue), so the R^2^
values describe the share of variance of two different variables.
Second, the log-log model uses fewer observations (519 instead of 808)
since movies with zero revenue or budget were dropped and set to NA.

Because the models cannot be compared on R² , we judge them on other
ground, and on those we consider the log model more appropriate. It
reduces the skewness of the revenue and the influence of extreme values
(like the Avengers), and it leaves out the zeros which most likely
represent missing data than true zero revenues or budgets. The
level-level model does include these zeros which may distort the
estimate of β₁. Therefore, we conclude that the log-log model fits
better eventough its R² is lower.

*step g*

```{r}
#WRITE YOUR CODE HERE
##test H0: beta=1 in the log-log model
b1_log<-coef(summary(model2))["log_budget","Estimate"]
se_log<-coef(summary(model2))["log_budget","Std. Error"]
t_log<-(b1_log-1)/se_log
t_log
2*pt(abs(t_log),df=df.residual(model2),lower.tail=FALSE)
##predicted revenue at average budget ($30 million)
exp(predict(model2,newdata=data.frame(log_budget=log(30000000))))
```

**Your Answer:**

We mostly agree with Chantal since in the level-level model (discussed
in question c) β₁=3.16 and we would reject H0:β₁\<=1. This means that on
average every extra dollar of budget goes together with more than one
extra dollar of revenue. In the log-log model the elasticity is around
1.03, which is not significantly different from 1 (t=0.66, p=0.51). This
shows that revenue rises proportionally with budget. At the average
budget of around \$30 million the model predicts a revenue of around
\$48millon, so an extra dollar of budget still goes together with about
\$1.65 (1.03 x 48/30) of extra revenue. In both models higher budgets do
not come with lower revenue. Therefore, Bob's claim that budgets are
"out of hand" is not supported by the data.

However, some caution is needed with this interpretation. First, the
models show correlation, not causation. The more expensive movies are
often blockbusters with famous actors and larger marketing campaigns
which can be a cause for the higher revenue. Second, revenue is not
profit: the marketing costs and the share that goes to cinemas is not
included. An elasticity of about 1 does mean that bigger budgets give no
advantage of scale, so revenue does not grow faster than budget. Third,
the average relationship hides large differences between movies, so
high-budget movies still carry risk.

Our advice would therefore be not to cut budgets or to focus on cheaper
movies, but to evaluate projects on expected profit rather than revenue
alone, and to invest in selectively high budget projects.

2

a.  Make a scatterplot with log revenue on the y-axis, and log budget on
    the x-axis. Within the same scatterplot, draw a straight line which
    summarizes the association between the log of revenue and log of
    budget. \textbf{[3 points]}
b.  Using the insights from the scatterplot, your linear model, and your
    data, find an example of a movie that vastly overperformed. That
    means, find a movie that had much more revenue than expected, given
    its budget. For this movie, report its log of revenue, its predicted
    log of revenue, and its residual. \textbf{[3 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE
plot(movies$log_budget,movies$log_revenue,
     main= "Log Revenue vs Log Budget",
     xlab= "Log (Budget)",
     ylab = "Log(Revenue)",
     pch=19,
     col= "hotpink")
abline(model2, col = "blue", lwd = 2)
```

**Your Answer:**

The scatter plot shows a positive and roughly linear association between
log budget and log revenue: the movies with a higher budget tend to earn
a higher revenue. The blue line is the fitted regression line, with an
intercept of -0.05 and a slope of 1.03. This means that a 1% increase of
budget is associated with a revenue that is 1.03% higher. The slope is
highly significant (p\<2e-16). The R-squared is 0.495, so the budget
explains half of the variation in log revenue. The points are spread
quite widely around the line, which shows that other factors have a
influence as well. The model uses 519 movies, because 289 movies with a
budget or revenue of zero (NA) were left out.

*step b*

```{r}
#WRITE YOUR CODE HERE
movies$pred_log_revenue<-predict(model2,newdata=movies)
movies$resid<-movies$log_revenue-movies$pred_log_revenue

print(head(movies[order(-movies$resid),c("title","budget","revenue","log_revenue","pred_log_revenue","resid")],5))



```

**Your Answer:**

The movie that over performed is the Full Monty, which had a budget of
\$3.5 million. The log revenue is 19.37, while the model predicted a log
revenue of only 15.47. The residual (19.37-15.47) is 3.89, which means
that the actual revenue was about 49 times higher than predicted since
its a log-log model (e\^3.89≈49). The model expected around \$5 million
in revenue, but the movie earned around \$258 million, which is far more
than expected given its budget. Primer has an almost identical residual
(3.89) but the prediction is less reliable because of a budget of only
\$7000. Therefore we chose The Full Monty as the clearest example.

# Week 5

a.  Make a frequency table of the variable genre. Which are the three
    genres that occur the most? \textbf{[2 points]}
b.  Create a new variable called genre2. Make sure that the three most
    popular genres remain the same, but that all the other genres get
    categorized into one genre called “Other”. Report a frequency table
    of this new variable genre2. \textbf{[2 points]}
c.  Estimate an OLS model which has as dependent variable the log of
    revenue of a movie, and as independent variable the log of budget, a
    dummy for each level that genre2 can take, and the year of release.
    Show a summary of the resulting model and interpret each
    coefficient. \textbf{[4 points]}

The movie studio that you work at is releasing a new movie in 2026. It
will be a Drama movie with a budget of 20,000,0000. It will have a
runtime of 120 minutes.

d.  Estimate a model that is able to predict the revenue of this movie.
    Give its predicted revenue and include a 90% prediction interval.
    \textbf{[5 points]}
e.  Plot the residuals against various independent variables in the
    model. Do you find any evidence of heteroskedasticity?
    \textbf{[2 points]}
f.  One executive at the studio wants to time the release of the movie
    to a specific month of the year such that they can maximize revenue.
    Another executive is of the opinion that the month in which the
    movie is released will not have a big impact on its revenue.
    Estimate a model that can test whether the month of release impacts
    the revenue of a movie. Use an appropriate hypothesis test to test
    whether month of release matters. What would you advise the movie
    studio regarding the timing of the release of the movie?
    \textbf{[5 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE
genre_table <- table(movies$genre)
genre_table_sorted <- sort(genre_table, decreasing = TRUE)
genre_table_sorted

```

**Your Answer:**

The frequency table shows that the three most common genres are drama:
402 movies, comedy: 186 movies and thriller with 116 movies.

*step b*

```{r}
#WRITE YOUR CODE HERE
top3 <- names(genre_table_sorted)[1:3]
top3

movies$genre2 <- ifelse(movies$genre %in% top3,movies$genre, "Other")
movies$genre2 <- as.factor(movies$genre2)

table(movies$genre2)
```

**Your Answer:**

The variable genre2 keeps Drama, Comedy and Thriller as separate
categories and all the other categories are grouped together under the
name "Other". The table shows 186 movies in Comedy, 402 in Drama, 104 in
Other and 116 in Thriller. The total is 808 movies.

*step c*

```{r}
#WRITE YOUR CODE HERE
movies_clean <- movies[movies$revenue > 0 & movies$budget > 0, ]

movies_clean$log_revenue <- log(movies_clean$revenue)
movies_clean$log_budget <- log(movies_clean$budget)

model <- lm(log_revenue ~ log_budget + genre2 + release_year, data = movies_clean) 
summary(model)

levels(movies_clean$genre2)

```

**Your Answer:**

Note that movies with a budget or revenue of zero were excluded, because
log() is undefined for these values. This causes the sample to be
reduced from 808 to 519 movies.

Comedy is the reference category.

**The estimated model is**: log(revenue) = 9.098 + 1.001\*log(budget) -
0.473\*genre2Drama - 0.014\*genre2Other - 0.322\*genre2Thriller -
0.004\*release_year

**Our interpretation of each coefficient:**

**Intercept (9.098, not significant)**: the predicted log(revenue) for a
Comedy movie when log(budget) and release_year are 0. This is not
practically meaningful on its own.

**log(budget) (1.001, p \< 0.001)**: this coefficient is highly
significant. A 1% increase in budget is associated with an approximately
1% increase in revenue, holding genre and release year constant. This
indicates a almost proportional relationship between budget and revenue.

**genre2Drama (-0.473, p = 0.004):** this is significant at the 1%
level. Drama movies are predicted to have a log(revenue) that is 0.473
lower than Comedy movies, holding budget and release year constant. This
means that on average drama films generate approximately (1 -
e\^(-0.473)) x 100 % ≈ 37.7 % less revenue than comedy films.

**genre2Other (-0.014, p = 0.949):** This coefficient is not
statistically significant. That means that there is no evidence that
movies in the "Other" genre category differ from Comedy movies in terms
of revenue, holding budget and release year constant.

**genre2Thriller (-0.322, p = 0.110):** not statistically significant at
the 5% level. Holding budget and release year constant, there is no
strong evidence that Thriller movies differ in revenue compared to
Comedy movies.

**release_year (-0.004, p = 0.669):** This coefficient is not
statistically significant, there is no evidence that the release is
associated with revenue, holding budget and genre constant.

The model has an R squared of 0.505, which means approximately 50.5% of
the variation in log(revenue) is explained by budget, release year and
genre. The overall model is highly significant. The results show that
budget is the strongest predictor of revenue. Genre matters mainly
through the Drama category, which is associated with significantly lower
revenue, while release year has no meaningful effect.

*step d*

```{r}
#WRITE YOUR CODE HERE
model_d <- lm(log_revenue ~ log_budget + genre2 + release_year + runtime, data = movies_clean)
summary(model_d)$r.squared

new_movie <- data.frame(
  log_budget = log(200000000),
  genre2 = "Drama",
  release_year = 2026,
  runtime = 120
)

pred <- predict(model_d, newdata = new_movie, interval = "prediction", level = 0.90)
exp(pred)
```

**Your Answer:**

For this step we used the model from part C, extended with runtime (120
minutes) and a budget of 200,000,000 (we assume that 20,000,0000 given
in the exercise is 200,000,000) for the drama movie released in 2026,
and predicted log revenue with predict(), which we transformed back to
revenue with exp(). We used a 90% prediction interval. The predicted
revenue of the movie is about 234.4 million (234,411,504). The 90%
prediction interval ranges from 19.5 million (19,507,130) to 2.82
billion (2,816,854,825). The interval is very wide because the model has
an R\^2 of 0.5056 and a large residual standard error (1.49 in logs), so
movies with the same budget, genre, year and runtime still differ a lot
in revenue. Also, a prediction interval is for one single movie, so it
includes the random difference of that specific movie. After
transforming back with exp(), this results in a very wide interval.

*step e*

```{r, fig.height=5, fig.width=7}
#WRITE YOUR CODE HERE

plot(movies_clean$log_budget, resid(model_d),
     xlab = "log_budget", ylab = "Residuals", main = "Residuals vs log budget",
     pch = 16, col = "hotpink")
abline(h = 0, col = "black", lwd = 2)

plot(movies_clean$release_year, resid(model_d),
     xlab = "release_year", ylab = "Residuals", main = "Residuals vs release year",
     pch = 16, col = "hotpink")
abline(h = 0, col = "black", lwd = 2)

plot(movies_clean$runtime, resid(model_d),
     xlab = "runtime", ylab = "Residuals", main = "Residuals vs runtime",
     pch = 16, col = "hotpink")
abline(h = 0, col = "black", lwd = 2)

boxplot(resid(model_d) ~ movies_clean$genre2,
        xlab = "genre2", ylab = "Residuals", main = "Residuals vs genre",
        col = "hotpink")
abline(h = 0, col = "black", lwd = 2)

```

**Your Answer:**

We plotted the residuals of the model against log budget, release year,
runtime and genre. If the errors have constant variance
(homoskedasticity), the residuals should be spread out evenly around
zero. In the plots we do not see a heteroskedasticity shape (the spread
does not get bigger or smaller as the variable changes). The spread
looks roughly constant, although it may be slightly smaller at the
highest budgets. Overall we find no clear evidence of
heteroskedasticity.

*step f*

```{r}
#WRITE YOUR CODE HERE
movies_clean$release_month <- factor(movies_clean$release_month)

model_f <- lm(log_revenue ~ log_budget + genre2 + release_year + runtime + release_month, data = movies_clean)

month_coefs <- summary(model_f)$coefficients[8:18, ]

month_table <- cbind(round(month_coefs[, 1, drop = FALSE], 3),
Pct_diff = round((exp(month_coefs[, 1]) - 1) * 100, 1), round(month_coefs[, 2:4], 3))
month_table

anova(model_d, model_f)
```

For this exercise we added the release month as a categorical variable
to the model of part d, so the model now contains log budget, genre,
release year, runtime and release month. To test whether the month of
release matters, we used an F-test that compares the model with and
without month (H0: all month coefficients are 0, H1: at least one month
coefficient is different from 0). The test gives F(11, 501) = 2.08, with
a p-value of 0.020. Since the p-value is below 0.05, we reject H0 in
favor of H1. This means that adding release month significantly improves
the model, suggesting that the month of release has a significant effect
on revenue. We would advise the studio, regarding the timing of the
release of the movie, to release it in November, December or May and to
avoid September. We advise these months because they have the highest
coefficients, which means that movies released in these months generate
more revenue than movies released in January (reference month), holding
the other variables constant. September has a negative coefficient, so
movies released in September generate less revenue than movies released
in January. The column Pct_diff shows the coefficients as a percentage
difference in revenue compared to January. For example, a movie released
in November earns about 55.8% more revenue than a movie released in
January. However, when we look at each month separately, none of the
differences is significant at the 5% level, so we cannot conclude with
confidence that these are the best or worst months for a movie release.
